\documentclass[a4paper,10pt]{article}
\usepackage[margin=1.28in]{geometry} 
\usepackage{hyperref}
\begin{document}

\section*{Purushottam Kumar}
\textbf{Phone:} +91 7033666962 \\
\textbf{Email:} purushottamkumar268@gmail.com \\
\textbf{Location:} Purnea, Bihar \\
\textbf{GitHub:} \href{https://github.com/kingmakerpratap}{github.com/kingmakerpratap} \\
\textbf{LinkedIn:} \href{https://www.linkedin.com/in/PurushottamKumarPratap}{linkedin.com/in/PurushottamKumarPratap}

\section*{Objective}
Aspiring Computer Science Engineer with strong foundation in programming, web development, and AI/ML.

\section*{Education}
- B.Tech in CSE, Govt. Engineering College Vaishali, 2024-27, CGPA 7.59 (till 4th sem) \\
- Diploma in CSE, Govt. Polytechnic Purnea, 2019-22, CGPA 7.93, 71.78% \\
- 10th, Shyama High School Bhatotar, 2019, 67.40%

\section*{Skills}
MS Word, Excel, PowerPoint, CorelDRAW, Photoshop, Canva, Tally Prime with GST

\section*{Technical Languages}
C, C++, Java, Python, HTML5, CSS3, JavaScript, PHP, MySQL

\section*{Projects}
- Library Book Entry System Website \\
- Commercial Online Shopping Website \\
- Live Voice-to-Text Caption Converter Website

\section*{Internships}
- Python Programming, Hypex Technology Pvt. Ltd. \\
- Full-Stack Web Development, ATPLC.in \\
- AI & ML, UniConverge Technologies Pvt. Ltd.

\section*{Achievements}
Strong academics, multiple internships, and hands-on projects.

\section*{Hobbies}
Problem Solving, Exploring Technologies, Chess, Cyber Security

\end{document}
